### 2015-03-04 paper_draft1.tex
tex files

\documentclass[12pt]{article}

%\usepackage{comment}
\usepackage{amsfonts}
%\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{epstopdf}
%\usepackage{parskip}

%\setlength{\textwidth}{6.2in}
%\setlength{\oddsidemargin}{0.2in}
%\setlength{\evensidemargin}{0in}
%\setlength{\textheight}{8.9in}
%\setlength{\voffset}{-1.0in}
%\setlength{\parindent}{20pt}
\setlength{\parindent}{1cm}
%\setlength{\mathindent}{1cm}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

\newcommand{\ba}{\begin{array}}
\newcommand{\ea}{\end{array}}

\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

\newcommand{\p}{\partial}
\newcommand{\pp}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\ppn}[3]{{\partial^{#1} #2 \over \partial #3^{#1}}}
\newcommand{\Pain}{Painlev\'{e} }

\newcommand{\mbf}[1]{\mbox{\boldmath {$#1$}}}
\newcommand{\tx}{\mbox}

\newcommand{\ol}{\overline}
\newcommand{\ft}{\widehat}
\newcommand{\mb}{\mathbb}

%\setlength{\parskip}{2mm}
\renewcommand{\theenumi}{\alph{enumi}}
\renewcommand{\labelenumi}{(\theenumi)}

\begin{document}

%\begin{center}
\title{\bf Adaptive Mesh Refinement for Hyperbolic PDE}
\author{}
\maketitle
%\end{center}

{\bf \abstractname{:}} {\small}

\section{Outline}
\begin{itemize}
\item

\end{itemize}

\end{document}

### 2015-03-04 paper_draft1.tex
outline 1

@@
 %\begin{center}
-\title{\bf Adaptive Mesh Refinement for Hyperbolic PDE}
+\title{\bf Adaptive Mesh Refinement for 1-D Hyperbolic PDE}
 \author{}
@@
 \begin{itemize}
-\item
+\item Overview of paper
+\begin{itemize}
+\item Description of AMR, Figure 2.1 from Berger-Leveque paper.
+\item Wave propagation form for 1-d equations. Updating on grid interfaces, section 4 of paper
+\item pseudo-code for algorithm, similar to that on page 2310 of paper.
+\item notes on: flagging cells, boundary conditions
+\end{itemize}
+\item Examples:
+\begin{itemize}
+\item scalar advection
+\item linear system (e.g. Acoustics)
+\item variable coefficient (e.g. Color equation)
+\item nonlinear scalar (burgers)
+\item nonlinear system (shallow water or acoustics with pressure term)
+\end{itemize}
 

### 2015-03-04 talk/talk.tex
group03 talk template

\documentclass{beamer}
\documentclass[xetex,mathserif,serif]{beamer}
\title[Crisis] % (optional, only for long titles)
{Adaptive Mesh Refinement}
\subtitle{1D Hyperbolic Problems}
\author[Author, A] % (optional, for multiple authors)
{S. Sinha\inst{1} \and K. J. Roche\inst{1,2}}
\institute[Universities Here and There] % (optional)
{
  \inst{1}%
  Department of Applied Mathematics\\
  University of Washington
  \and
  \inst{2}%
  High Performance Computing\\
  Pacific Northwest National Laboratory
}
\date[KPT 2004] % (optional)
{Presentation to AM574, Prof. R. J. Leveque presiding}
\subject{Computer Science}

\begin{document}
\frame{\titlepage}

  %get references out of the way first 
  \begin{frame}[allowframebreaks]
  \frametitle<presentation>{Main References for this Talk}    
  \begin{thebibliography}{10}    
%  \beamertemplatebookbibitems
 % \bibitem{Autor1990}
  %  A.~Autor.
   % \newblock {\em Introduction to Giving Presentations}.
    %\newblock Klein-Verlag, 1990.
  \beamertemplatearticlebibitems
  \bibitem{Berger1998}
    M.~Berger and R.~Leveque 
    \newblock Adaptive Mesh Refinement Using Wave-Propagation Algorithms for Hyperbolic Systems
    \newblock {\em SIAM J. Numer. Anal.}, 35(6):2298--2316, 1998.
  \end{thebibliography}
\end{frame}

%outline
  \begin{frame}
    \frametitle{Talk Outline}
    \begin{itemize}
    \item{Overview of Berger and Leveque AMR paper}
    \item{wave propagation formulation}
    \item{etc.}
    \end{itemize}
    %Content goes here
  \end{frame}

  \begin{frame}{Figure Example}
  The question is how does beamerclass place this ???
          \includegraphics[height=2.5cm,width=10cm]{corrected-titan-4cmp-abm-cpu-gpu.png}
\end{frame}

  %frames with figures ... 
  \begin{frame}{Example of columns 1}
    \begin{columns}[c] % the "c" option specifies center vertical alignment
    \column{.5\textwidth} % column designated by a command
     Contents of the first column
    \column{.5\textwidth}
     Contents split \\ into two lines
    \end{columns}
\end{frame}

  %basic frame structure 
  \begin{frame}
    \frametitle{This is the second slide}
    \framesubtitle{A bit more information about this}
    %More content goes here
  \end{frame}
  \begin{frame}[fragile]

% for source code reference if needed -still not happy with this yet but we have time ... 
\frametitle{Source code}

\begin{lstlisting}[caption=First C example]
int main()
{
    printf("Hello World!");
    return 0;
}
\end{lstlisting}
\end{frame}
% etc
\end{document}

### 2015-03-04 paper_draft1.tex
modified paper outline

--- 2015-03-04 paper_draft1.tex
@@
 %\begin{center}
-\title{\bf Adaptive Mesh Refinement for Hyperbolic PDE}
-\author{}
+\title{\bf Adaptive Mesh Refinement for 1-D Hyperbolic PDEs}
+\author{ 
+Saumya Sinha\footnote{Department of Applied Mathematics, University of Washington, Seattle, Washington
+U.S.A.
+Email:\texttt{saumya@uw.edu}},
+Kenneth J. Roche\footnote{
+High Performance Computing Group, 
+Pacific Northwest National Laboratory,
+1 Battelle Road,
+Richland, Washington 
+U.S.A. 
+Email:\texttt{kenneth.roche@pnnl.gov}} 
+}
 \maketitle
@@
 
-\section{Outline}
-\begin{itemize}
-\item
+\newpage
+\tableofcontents
+\listoffigures
+\listoftables
+\newpage
 
-\end{itemize}
+\section{Overview of Paper}
+\subsection{Description of AMR (Fig 2.1 from Berger-Leveque)}
+\subsection{Wave-propagation for 1D equations -updating grid interfaces (section 4 of paper)}
+\subsection{Pseudo-code for AMR}
+\subsection{Comment on determining refinement - error estimation}
+\subsection{Notes on flagging cells, boundary conditions}
+
+\section{Examples of 1D AMR}
+\subsection{scalar advection}
+\subsection{linear system (acoustics)}
+\subsection{variable coefficient (color equation)}
+\subsection{nonlinear scalar (Burgers)}
+\subsection{nonlinear system (shallow water or acoustics with pressure term)}
+
+\section{Results}
+\subsection{Numerical experiments for the 1D cases}
+\subsection{Software implementation}
+
+\section{Summary}
+
+%\section{Outline}
+%\begin{itemize}
+%\item Overview of paper
+%\begin{itemize}
+%\item Description of AMR, Figure 2.1 from Berger-Leveque paper.
+%\item Wave propagation form for 1-d equations. Updating on grid interfaces, section 4 of paper
+%\item pseudo-code for algorithm, similar to that on page 2310 of paper.
+%\item comment on error estimation -determining refinement
+%\item notes on: flagging cells, boundary conditions
+%\end{itemize}
+%\item Examples of 1D AMR
+%\begin{itemize}
+%\item scalar advection
+%\item linear system (e.g. Acoustics)
+%\item variable coefficient (e.g. Color equation)
+%\item nonlinear scalar (burgers)
+%\item nonlinear system (shallow water or acoustics with pressure term)
+%\end{itemize}
+%\item Results of Numerical Experiments for the 1D cases
+%\item Software 
+%
+%\end{itemize}
 

### 2015-03-04 paper_draft1.tex
paper outline -needs some work still
paper --added some equations and tweaked the outline

@@
 \subsection{scalar advection}
+We study here the 1D scalar advection equation
+\begin{equation}
+q(x,t)_{t} + \bar{u} q(x,t)_{x}=0
+\end{equation}
+where $\bar{u}$ is a constant representing the velocity of displacement. Let $\bar{u}>0$ for simplicity (right going).
+
+\subsection{variable coefficient (color equation)}
+We study here the 1D scalar problem of the form
+\begin{equation}
+q(x,t)_{t} + u(x) q(x,t)_{x}=0
+\end{equation}
+\noindent where now the velocity is allowed to vary as a function of its position. This is sometimes called the {\it color} equation.
+
+\subsection{nonlinear scalar (Burgers)}
+We study here the 1D systems derived from the conservative, 
+\begin{equation}
+q(x,t)_{t} + f(q(x,t))_{x}=0
+\end{equation}
+which can be cast in non-conservative, quasilinear form 
+ \begin{equation}
+q(x,t)_{t} + f'(q(x,t))q(x,t)_{x}=0 .
+\end{equation}
+In Burgers inviscid equation, $f(q(x,t))=\frac{1}{2}q^2$.
+
 \subsection{linear system (acoustics)}
-\subsection{variable coefficient (color equation)}
-\subsection{nonlinear scalar (Burgers)}
+We study here the 1D systems of the form
+\begin{equation}
+q(x,t)_{t} + A q(x,t)_{x}=0
+\end{equation}
+\noindent and $A$ satisfies hyperbolicity conditions.
+
 \subsection{nonlinear system (shallow water or acoustics with pressure term)}
+We use the formulation in chapter 13 of \cite{levFVMHP} to describe the shallow water equations.
+So,
+
+\begin{equation}
+\left( \begin{array}{c}
+h  \\
+h u\end{array} \right)_{t} + 
+\left( \begin{array}{c} 
+hu \\
+hu^2 + \frac{1}{2}gh^2\end{array} \right)_{x} = 0
+\end{equation}
+
+\noindent where $h$ is the height (or depth) of the fluid, $u$ is the horizontal component of the velocity, and $hu$ is the discharge -i.e.
+the flow rate of the fluid past a point.
+One can assign the state variables $(q^1,q^2)$, and the flux $f$ as follows:
+
+\begin{equation}
+q(x,t)=\left( \begin{array}{c}
+h  \\
+h u\end{array} \right)_{t} 
+=
+\begin{equation}
+\left( \begin{array}{c}
+q^1  \\
+q^2\end{array} \right) 
+\end{equation}
+\noindent and
+
+\begin{equation}
+f(q(x,t))=
+\left( \begin{array}{c} 
+hu \\
+hu^2 + \frac{1}{2}gh^2\end{array} \right)
+= 
+\left( \begin{array}{c} 
+q^2 \\
+(q^2)^2 / q^1 + \frac{1}{2}g (q^1)^2\end{array} \right)
+\end{equation}
+\noindent to be consistent with state notation from previous sections of this report.
 
@@
 
+%kr -just let the TOC do the outline for us and track our changes at compile time 
+%also, I added a couple of bullets since our discussion this afternoon
 %\section{Outline}
@@
 
+\begin{thebibliography}{9}
+\bibitem{levFVMHP}  
+  R.~Leveque
+Finite Volume Methods for Hyperbolic Problems
+ Cambridge University Press (2002)  \\
+
+\bibitem{CCS:staff}
+ S.~Carter, N.~Rao,
+ Private Communication.
+
+\end{thebibliography}
+
 \end{document}

### 2015-03-05 paper_draft1.tex
paper --added some equations and tweaked the outline
paper --error estimation, references, 1d advection

@@
-\documentclass[12pt]{article}
+\documentclass[12pt,leqno]{article}
 
@@
 
-{\bf \abstractname{:}} {\small}
+{\bf \abstractname{: In this paper we describe an adaptive mesh refinement algorithm that extends high resolution wave-progpagation techniques to hyperbolic systems in non-conservative form.
+The method for keeping numerical conservation at grid cell interfaces is described.
+The algorithm was (will be) tested for simple 1D scalar linear and non-linear problems, and to some simple systems.
+Results will be compared to static mesh solutions for the same problems computed with Clawpack\cite{claw}.}} {\small}
 
@@
 \subsection{Description of AMR (Fig 2.1 from Berger-Leveque)}
+An adaptive mesh refinement strategy that uses rectangular patches over Cartesian grids to refine both space and time coordinates is useful for modeling and tracking regions where the solutions are not smooth such as exhibited around shocks.
+
+The idea behind the refinement step comes from first determining where a refinement may be useful.
+
+We will examine figure \ref{fig21}:
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=.65\textwidth]{berg-lev-fig21}
+    \caption{essential figure for adapting cartesian grids}
+    \label{fig21}
+\end{figure}
+
 \subsection{Wave-propagation for 1D equations -updating grid interfaces (section 4 of paper)}
@@
 \subsection{Comment on determining refinement - error estimation}
-\subsection{Notes on flagging cells, boundary conditions}
+If the solution $q(x,t)$ is smooth enough, assume that our difference method $D$ has order of accuracy $s$ in both 
+space and time, then the local truncation error is $q(x,t+k) -D q(x,t) = \tau(x,t) + k O(k^{s+1}+h^{s+1}))$ where $\tau$ is the leading error.
+Taking two time steps suggests $q(x,t+2k) -D^2 q(x,t) = 2\tau(x,t) + k O(k^{s+1}+h^{s+1}))$.
+Now, suppose we consider coarsening our grid to have space and time widths $2h$, $2k$ respectively.
+Let the differencing scheme be called $D_{2h}$ in this case.
+The local truncation error in this case reads $q(x,t+2k) -D_{2h} q(x,t) = 2^{s+1}\tau(x,t) + O(h^{s+2})$.
+Thus, an error growth estimate at time $t$ can be formed by taking the difference in the error present taking two steps with the regular integration scheme, and a single large step using every other grid point:
+
+\begin{equation}
+\frac{D^2 q(x,t) - D_{2h} q(x,t)}{2^{s+1}-2} = \tau(x,t) + O(h^{s+2})
+\end{equation}
+
+This procedure is easily implemented in AMR.
+The values on a grid at a given level are projected onto a virtual grid coarsened by a factor of two in each direction.
+The solution on both grids is advanced in time: the original grid for two time steps, the coarsened grid for one step using a time step twice as large.
+The difference between the solutions obtained on the two grids at each point is proportional to the local truncation error at that point.
+At coarse cells where the difference between the two sets of values exceed some tolerance, all four cells contained in the real grid are flagged as requiring refinement.
+One disadvantage of this procedure is that it always predicts a large error in the neighborhood of captured discontinuities.
+It is easy to construct examples for which the procedure outlined above will give values on the coarsened grid which differ pointwise by an amount independent of the mesh spacing in the neighborhood of a shock.
+In general, this leads to refinement of the mesh at all discontinuities with strength greater than some minimum.
+See \cite{berg-coll} for more details.
+
+\subsection{Note on boundary conditions}
 
@@
 \subsection{scalar advection}
-We study here the 1D scalar advection equation
+The simplest problem (and most boring) is the 1D scalar advection equation
 \begin{equation}
@@
 where $\bar{u}$ is a constant representing the velocity of displacement. Let $\bar{u}>0$ for simplicity (right going).
+The Riemann problem in this case consists of adding the initial conditions:
+\begin{equation}
+q(x,0):= \phi(x)=
+\left\{ \begin{array}{c}
+q_l , \, \, \, \, x<0\\
+q_r , \, \, \, \, x>0\end{array}\right 
+\end{equation}
+\noindent Here the coefficient matrix is the number $\bar{u}$ which has eigenvalue $\lambda^1 = \bar{u}$ and eigenvector $r^1 =1$ and the jump discontinuity determined by $q_r - q_l$ propagates with speed $\lambda^1$ along characteristics.
+The solution is
+\begin{equation}
+q(x,t):= \phi(x-\lambda^1 t) \, .
+\end{equation}
 
@@
 h  \\
-h u\end{array} \right)_{t} 
+h u\end{array} \right)
 =
@@
 \subsection{Numerical experiments for the 1D cases}
+\subsection{AMR versus fixed mesh Riemann solvers}
 \subsection{Software implementation}
@@
 \begin{thebibliography}{9}
+\bibitem{claw}
+http://www.clawpack.org\\
+
 \bibitem{levFVMHP}  
@@
 
-\bibitem{CCS:staff}
- S.~Carter, N.~Rao,
- Private Communication.
+\bibitem{berg-coll}
+M.~Berger and P.~Collela, Local Adaptive Mesh Refinement for Shock Hydrodynamics
+Journal of Computational Physics 82, 64-84 (1989)\\
+
+\bibitem{Berger1998}
+M.~Berger and R.~Leveque, Adaptive Mesh Refinement Using Wave-Propagation Algorithms for Hyperbolic Systems
+SIAM Journal of Numerical Analysis, 35(6):2298--2316, (1998)\\
+
+\bibitem{Berger1982}
+M.~Berger, Adaptive Mesh Refinement for Hyperbolic Partial Differential Equations,
+ {\em PhD Thesis}, Department of Computer Science, Stanford University, Stanford, CA 94305 (1982)\\
 

### 2015-03-05 paper_draft1.tex
paper --error estimation, references, 1d advection

@@
 This procedure is easily implemented in AMR.
-The values on a grid at a given level are projected onto a virtual grid coarsened by a factor of two in each direction.
+The values on a grid at a given level are projected, i.e.
+Richardson extrapolation, onto a virtual grid coarsened by a factor of two in each direction.
 The solution on both grids is advanced in time: the original grid for two time steps, the coarsened grid for one step using a time step twice as large.
@@
 \section{Results}
-\subsection{Numerical experiments for the 1D cases}
-\subsection{AMR versus fixed mesh Riemann solvers}
 \subsection{Software implementation}
+Clawpack was used to generate numerical Riemann solutions to our test problems for the fixed mesh case.
+We utilized (Python, Matlab, C) for our AMR implementations.
+Please find our software here: (need software + examples ...) and use the \texttt{Readme.txt} file there 
+to build and test the software. The test cases presented in this report are reproduced there.
+\subsection{Results of the Numerical experiments for the 1D cases}
 
 \section{Summary}
+In this paper we described the adaptive mesh refinement algorithm presented in \cite{Berger1998}, and tested the 
+algorithm for several simplistic 1D cases. Our results were compared against those from Clawpack. Our AMR 
+implementations are available to anyone who wants them.
 

### 2015-03-05 paper_draft1.tex
paper --error estimation, references, 1d advection

@@
 
-The idea behind the refinement step comes from first determining where a refinement may be useful.
+The idea behind the refinement step comes from first determining where a refinement may be useful. See section \ref{whentorefine} for details.  Examine figure \ref{fig21}.
+We need to explain how to preserve conservation of flux at grid interfaces.
+There are essentially three cases to consider: coarse cell to coarse cell, fine cell to fine cell, and coarse cell to fine cell.
+Let $F_i$ be the flux at the left edge of coarse cell $i$.
+This is different than what we typically wrote in class, $F_{i-\frac{1}{2}}$, for convenience.
+Thus, updating between coarse grid cells is simply:
+\begin{equation}
+q_{i}^{1} = q_{i}^{0} - \frac{k}{h} (F_{i+1}^{0} - F_{i}^{0}) 
+\end{equation}
+\noindent where $h,k$ are the space and time lattice spacing respectively.
 
-We will examine figure \ref{fig21}:
+In regions that contain $m$ adjacent single level refined cells let the lattice spacing be denoted by $\hat{h},\hat{k}$ respectively.
+We have $\forall i=1,m$
+\begin{equation}
+\begin{array}{c}
+\hat{q}_{i}^{1} = \hat{q}_{i}^{0} - \frac{\hat{k}}{\hat{h}} (\hat{F}_{i+1}^{0} - \hat{F}_{i}^{0}) \\
+\hat{q}_{i}^{2} = \hat{q}_{i}^{1} - \frac{\hat{k}}{\hat{h}} (\hat{F}_{i+1}^{1} - \hat{F}_{i}^{1}) 
+\end{array}
+\end{equation}
+\noindent in the refined cells where we assume each refinement is $2X$.
+
+In regions where the coarse and fine grids overlap, care must be taken. Two ghost cells are introduced, $\hat{q}_{m+1},\hat{q}_{m+2}$. The values in these 
+cells are decided by interpolating the coarse values  $q_{i}^{0}, q_{i}^{1}$. At the final time (completed time step)  $q_{i}^{1}$ is replaced by the average of the 
+fine grid values in the overlapped region:
+\begin{equation}
+q_{j-1}^{1} = \frac{1}{2} (\hat{q}_{m+1}^{2}+\hat{q}_{m+2}^{2})
+\end{equation}
+\noindent and the corresponding left edge flux is similarly modified so that $q_{i}^{1}$ is finally modified as:
+\begin{equation}
+q_{i}^{1} \rightarrow q_{i}^{1} + \frac{k}{h} ( \frac{1}{2}(\hat{F}_{m+1}^{0} - \hat{F}_{m+1}^{1}) - F_{i}^{0}) \, .
+\end{equation}
+
 \begin{figure}[h]
@@
 \subsection{Pseudo-code for AMR}
-\subsection{Comment on determining refinement - error estimation}
+\subsection{Comment on determining refinement - error estimation}\label{whentorefine}
 If the solution $q(x,t)$ is smooth enough, assume that our difference method $D$ has order of accuracy $s$ in both 
@@
 
-This procedure is easily implemented in AMR.
-The values on a grid at a given level are projected, i.e.
+Thus, the values on a grid at a given level are projected, i.e.
 Richardson extrapolation, onto a virtual grid coarsened by a factor of two in each direction.
-The solution on both grids is advanced in time: the original grid for two time steps, the coarsened grid for one step using a time step twice as large.
+The solutions on both grids are advanced in time: the original grid for two time steps, the coarsened grid for one step using a time step twice as large.
 The difference between the solutions obtained on the two grids at each point is proportional to the local truncation error at that point.
@@
 It is easy to construct examples for which the procedure outlined above will give values on the coarsened grid which differ pointwise by an amount independent of the mesh spacing in the neighborhood of a shock.
-In general, this leads to refinement of the mesh at all discontinuities with strength greater than some minimum.
 See \cite{berg-coll} for more details.
+A buffer zone around the flagged cells is added to track features of interest in the refined region.
+This buffer zone must be affiliated with the number of time steps evaluated at a particular level.
+If a patch at level $L$ is refined by even integer $R_L$, then the time-step is equally refined implying that $R_L$ steps must be taken on the refined grid at level $L+1$ for each step on grid at level $L$.
 

### 2015-03-06 paper_draft1.tex
paper --error estimation, references, 1d advection

@@
 \section{Overview of Paper}
-\subsection{Description of AMR (Fig 2.1 from Berger-Leveque)}
 An adaptive mesh refinement strategy that uses rectangular patches over Cartesian grids to refine both space and time coordinates is useful for modeling and tracking regions where the solutions are not smooth such as exhibited around shocks.
-
-The idea behind the refinement step comes from first determining where a refinement may be useful. See section \ref{whentorefine} for details.  Examine figure \ref{fig21}.
-We need to explain how to preserve conservation of flux at grid interfaces.
+\subsection{Flux updates on refined and coarse meshes}
+The idea behind the refinement step comes from first determining where a refinement may be useful. See section \ref{whentorefine} for details.  
+We need to explain how to preserve conservation of flux at grid interfaces, Fig \ref{fig21}.
 There are essentially three cases to consider: coarse cell to coarse cell, fine cell to fine cell, and coarse cell to fine cell.
@@
 \noindent and the corresponding left edge flux is similarly modified so that $q_{i}^{1}$ is finally modified as:
-\begin{equation}
+\begin{equation}\label{fluxcorrect}
 q_{i}^{1} \rightarrow q_{i}^{1} + \frac{k}{h} ( \frac{1}{2}(\hat{F}_{m+1}^{0} - \hat{F}_{m+1}^{1}) - F_{i}^{0}) \, .
@@
     \includegraphics[width=.65\textwidth]{berg-lev-fig21}
-    \caption{essential figure for adapting cartesian grids}
+    \caption{Essential figure for flux adapting Cartesian grids.
+The top grid is the normal coarse grid we are used to using with fluxes indicated.
+The middle diagram shows the case where a fine grid overlays a coarse grid and the interface region of fine and coarse grids.
+Recall that $2\hat{h}=h$ and $2\hat{k}=k$.
+The bottom diagram depicts the ghost cell region imposed on the coarse cell interface as well as the fine grid fluxes needed to bridge the interface.}
     \label{fig21}
@@
 
-\subsection{Wave-propagation for 1D equations -updating grid interfaces (section 4 of paper)}
+\subsection{Updating grid interfaces with wave propagation}
+For conservation laws we have developed wave propagation methods in class whereby a Riemann problem is solved at each interface between grid cells.
+These methods can be extended beyond the linear accuracy to second order accuracy and controlled with limiters where smooth to discontinuous transitions occur.
+Wave propagation algorithms are written in a manner that they can be extended to hyperbolic problems not in conservation form retaining wave features but with no flux function.
+
+With flux-differencing to ensure conservation a new coarse grid value is updated by an average of fine-grid values in any cell covered by a fine grid.
+The key to conservation is that flux into coarse cells is accounted for by flux out of adjacent fine cells, and vice versa.
+For wave-propagation algorithms, a similar correction is needed for the waves to yield conservation.
+The wave-propagation form can be used to update the values at the interface between fine and coarse grid cells on each grid independently using Òghost-cellÓ values as needed near grid interfaces.
+
+Whether conservative or non-conservative systems are treated, second-order corrections are still written as flux-differences and utilize the flux correction as eqn(\ref{fluxcorrect}). 
+However, the first-order upwind terms written in terms of the fluctuations must be handled differently.
+
+To maintain conservation we must {\it first} solve the Riemann problem between the ghost cell value $\hat{q}_{m+1}^{0}$ on the fine grid and the coarse grid value $q_{j}^{0}$, and add to the coarse cell value $q_{j}^{1}$ the resulting total fluctuation $A^{-}\Delta q + A^{+}\Delta q$ weighted by $\hat{k}/h = 1/2$ since the time step is $\hat{k}$ while the cell size is $h$.
+{\it Second} we must also solve a Riemann problem on the fine grid between $\hat{q}_{m+1}^{1}$ and $q_{j}^{0}$
+and add these fluctuations into $q_{j}^{1}$.
+
+The correction step extends to an arbitrary hyperbolic system where we use a Riemann solver to obtain $A^{-}\Delta q$ and  $A^{+}\Delta q$ from the two states $\hat{q}_{m+1}^{0}$ and $q_{j}^{0}$.
+This step is made in each of the $R$ time steps on the refined grid within the single coarse-grid step, where $R$ is the refinement ratio ($2X$ in our examples so far).
+\\
+
+\noindent The fix-up algorithm:
+\begin{description}
+  \item[for $N = 0 , R-1$] \hfill \\
+  solve the Riemann problem with data $\hat{q}_{m+1}^{N}$ and $q_{j}^{0}$ to compute $A^{-}\Delta q$ and  $A^{+}\Delta q$\\ \hfill
+  update $q_{j}^{1} \rightarrow q_{j}^{1} + \frac{\hat{k}}{h}$ ($A^{-}\Delta q + A^{+}\Delta q$)
+\end{description}
+
 \subsection{Pseudo-code for AMR}
@@
 Thus, an error growth estimate at time $t$ can be formed by taking the difference in the error present taking two steps with the regular integration scheme, and a single large step using every other grid point:
+
+A similar modification must be made in each of the R time steps on the refined grid within the single coarse-grid step, where R is again the refinement ratio. The fix-up algorithm thus takes the form
+?for N = 0, 1, . . . , R ? 1 do
+solve the Riemann problem with data qö and q
+to compute A?Æq and A+Æq, update q1 := q1 + kö (A?Æq + A+Æq).
+jjh
+For the case of a conservation law, this will restore conservation, and, in fact, agrees
+with the flux function modification (2.4) if numerical fluxes are defined by (3.9).
+Note that, in view of (3.8), in the conservation law case the coarse-grid value qj1 is
+N0
+simply updated by the entire flux difference f (qö ) ? f (q ), and we wouldnÕt need
+m+1 j
+to actually solve the Riemann problem. However, implementing it as presented above
+gives a uniform and general formulation.
 

### 2015-03-06 paper_draft1.tex
paper --error estimation, references, 1d advection

@@
 \subsection{Flux updates on refined and coarse meshes}
-The idea behind the refinement step comes from first determining where a refinement may be useful. See section \ref{whentorefine} for details.  
-We need to explain how to preserve conservation of flux at grid interfaces, Fig \ref{fig21}.
+The idea behind the refinement step comes from first determining where a refinement may be useful, see section \ref{whentorefine} for details.  
+Here we explain how to preserve conservation of flux at grid interfaces and refer to Fig \ref{fig21}.
 There are essentially three cases to consider: coarse cell to coarse cell, fine cell to fine cell, and coarse cell to fine cell.
 Let $F_i$ be the flux at the left edge of coarse cell $i$.
-This is different than what we typically wrote in class, $F_{i-\frac{1}{2}}$, for convenience.
-Thus, updating between coarse grid cells is simply:
+This is different notation than what we typically wrote in class, $F_{i-\frac{1}{2}}$.
+
+Updating between coarse grid cells is simply:
 \begin{equation}
@@
 
-In regions that contain $m$ adjacent single level refined cells let the lattice spacing be denoted by $\hat{h},\hat{k}$ respectively.
-We have $\forall i=1,m$
+In regions that contain $m$ adjacent single level refined cells let the lattice spacing be denoted by $\hat{h},\hat{k}$.
+We have, in the stated order, $\forall i=1,m$
 \begin{equation}
@@
 The correction step extends to an arbitrary hyperbolic system where we use a Riemann solver to obtain $A^{-}\Delta q$ and  $A^{+}\Delta q$ from the two states $\hat{q}_{m+1}^{0}$ and $q_{j}^{0}$.
-This step is made in each of the $R$ time steps on the refined grid within the single coarse-grid step, where $R$ is the refinement ratio ($2X$ in our examples so far).
+This step is made in each of the $R$ time steps on the refined grid within the single coarse-grid step, where $R$ is the refinement ratio.
 \\
@@
 Taking two time steps suggests $q(x,t+2k) -D^2 q(x,t) = 2\tau(x,t) + k O(k^{s+1}+h^{s+1}))$.
-Now, suppose we consider coarsening our grid to have space and time widths $2h$, $2k$ respectively.
-Let the differencing scheme be called $D_{2h}$ in this case.
+Now, coarsen the grid to have space and time widths $2h$, $2k$ and let the differencing scheme be called $D_{2h}$ in this case.
 The local truncation error in this case reads $q(x,t+2k) -D_{2h} q(x,t) = 2^{s+1}\tau(x,t) + O(h^{s+2})$.
-Thus, an error growth estimate at time $t$ can be formed by taking the difference in the error present taking two steps with the regular integration scheme, and a single large step using every other grid point:
-
-A similar modification must be made in each of the R time steps on the refined grid within the single coarse-grid step, where R is again the refinement ratio. The fix-up algorithm thus takes the form
-?for N = 0, 1, . . . , R ? 1 do
-solve the Riemann problem with data qö and q
-to compute A?Æq and A+Æq, update q1 := q1 + kö (A?Æq + A+Æq).
-jjh
-For the case of a conservation law, this will restore conservation, and, in fact, agrees
-with the flux function modification (2.4) if numerical fluxes are defined by (3.9).
-Note that, in view of (3.8), in the conservation law case the coarse-grid value qj1 is
-N0
-simply updated by the entire flux difference f (qö ) ? f (q ), and we wouldnÕt need
-m+1 j
-to actually solve the Riemann problem. However, implementing it as presented above
-gives a uniform and general formulation.
-
+Thus, an error growth estimate at time $t$ can be formed by taking the difference in the error taking two steps with the regular integration scheme, and a single large step using every other grid point:
 \begin{equation}
-\frac{D^2 q(x,t) - D_{2h} q(x,t)}{2^{s+1}-2} = \tau(x,t) + O(h^{s+2})
+\frac{D^2 q(x,t) - D_{2h} q(x,t)}{2^{s+1}-2} = \tau(x,t) + O(h^{s+2}) \, .
 \end{equation}
-
-Thus, the values on a grid at a given level are projected, i.e.
+The values on a grid at a given level are projected, i.e.
 Richardson extrapolation, onto a virtual grid coarsened by a factor of two in each direction.

### 2015-03-06 paper_draft1.tex
Minor syntax changes

@@
-\documentclass[12pt,leqno]{article}
+\documentclass[11pt,leqno]{article}
 
@@
 
-{\bf \abstractname{: In this paper we describe an adaptive mesh refinement algorithm that extends high resolution wave-progpagation techniques to hyperbolic systems in non-conservative form.
+{\small {\bf \abstractname}{: In this paper we describe an adaptive mesh refinement algorithm that extends high resolution wave-progpagation techniques to hyperbolic systems in non-conservative form.
 The method for keeping numerical conservation at grid cell interfaces is described.
 The algorithm was (will be) tested for simple 1D scalar linear and non-linear problems, and to some simple systems.
-Results will be compared to static mesh solutions for the same problems computed with Clawpack\cite{claw}.}} {\small}
+Results will be compared to static mesh solutions for the same problems computed with Clawpack\cite{claw}.}}
 
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=.65\textwidth]{berg-lev-fig21}
-    \caption{Essential figure for flux adapting Cartesian grids.
+%\begin{figure}[h]
+   % \centering
+    %\includegraphics[width=.65\textwidth]{berg-lev-fig21}
+   % \caption{Essential figure for flux adapting Cartesian grids.
 The top grid is the normal coarse grid we are used to using with fluxes indicated.
@@
 The bottom diagram depicts the ghost cell region imposed on the coarse cell interface as well as the fine grid fluxes needed to bridge the interface.}
-    \label{fig21}
-\end{figure}
+    %\label{fig21}
+%\end{figure}
 
@@
 q_l , \, \, \, \, x<0\\
-q_r , \, \, \, \, x>0\end{array}\right 
+q_r , \, \, \, \, x>0\end{array}\right. 
 \end{equation}
+
 \noindent Here the coefficient matrix is the number $\bar{u}$ which has eigenvalue $\lambda^1 = \bar{u}$ and eigenvector $r^1 =1$ and the jump discontinuity determined by $q_r - q_l$ propagates with speed $\lambda^1$ along characteristics.
@@
 =
-\begin{equation}
 \left( \begin{array}{c}

### 2015-03-06 paper_draft1.tex
paper --correct indices in some eqns

--- 2015-03-06 paper_draft1.tex
@@
 \begin{equation}\label{fluxcorrect}
-q_{i}^{1} \rightarrow q_{i}^{1} + \frac{k}{h} ( \frac{1}{2}(\hat{F}_{m+1}^{0} - \hat{F}_{m+1}^{1}) - F_{i}^{0}) \, .
+q_{i}^{1} \rightarrow q_{i}^{1} + \frac{k}{h} ( \frac{1}{2}(\hat{F}_{m+1}^{0} + \hat{F}_{m+1}^{1}) - F_{i}^{0}) \, .
 \end{equation}

### 2015-03-08 paper_draft1.tex
paper --figure 2.1
paper --kr + ss update amr alg
paper --tex style change
paper -changed outline slightly and edited

@@
 %\setlength{\parindent}{20pt}
-\setlength{\parindent}{1cm}
+%\setlength{\parindent}{1cm}
+\setlength{\textwidth}{6.2in}
+\setlength{\oddsidemargin}{0in}
+\setlength{\evensidemargin}{0in}
+\setlength{\textheight}{9in}
+\setlength{\voffset}{-.9in}
+\setlength{\headsep}{26pt}
 %\setlength{\mathindent}{1cm}
@@
 
-{\small {\bf \abstractname}{: In this paper we describe an adaptive mesh refinement algorithm that extends high resolution wave-progpagation techniques to hyperbolic systems in non-conservative form.
+{\small {\bf \abstractname}{: We describe an adaptive mesh refinement algorithm that extends high resolution wave-progpagation techniques to hyperbolic systems in non-conservative form.
 The method for keeping numerical conservation at grid cell interfaces is described.
-The algorithm was (will be) tested for simple 1D scalar linear and non-linear problems, and to some simple systems.
-Results will be compared to static mesh solutions for the same problems computed with Clawpack\cite{claw}.}}
+The algorithm was tested for simple 1D problems.
+Results are compared to static mesh solutions for the same problems computed with Clawpack\cite{claw}.}}
 
-\newpage
 \tableofcontents
@@
 An adaptive mesh refinement strategy that uses rectangular patches over Cartesian grids to refine both space and time coordinates is useful for modeling and tracking regions where the solutions are not smooth such as exhibited around shocks.
+We present an AMR algorithm in the next section, and provide details in subsequent sections for the various steps.
+
+\section{Pseudo-code for AMR}
+\noindent Steps for the AMR algorithm:
+\begin{enumerate}
+\item{initialize coarse grid}
+\item{evolve time on coarse grid}
+\item{{\it recurse}: estimate error, create fine grid}
+\begin{itemize}
+\item{cell flagging}
+\item{clustering}
+\item{fine grid generation}
+\end{itemize}
+\item{solve Riemann on refined grid levels}
+\item{correction step to ensure conservation}
+\item{go to step {\it b} }
+\end{enumerate}
+
+\subsection{wave propagation algorithm to evolve time}
+After initializing the discrete coarse grid, a standard high resolution wave propagation including limiter corrections to evolve our Riemann problem is employed.
+The method reads,  i.e.
+for the {\it color} eqn (see \ref{color}):
+\begin{equation} \label{hires}
+ q_{i}^{n+1} = q_{i}^{n} - \frac{k}{h}(u_{i}^{+}(q_{i}^{n}-q_{i-1}^{n})+u_{i}^{-}(q_{i+1}^{n}-q_{i}^{n})) - \frac{k}{h}(\tilde{F_{i+1}} - \tilde{F_{i}})
+ \end{equation}
+ \noindent where 
+ \begin{equation}
+\tilde{F_{i}} = \frac{1}{2}\vert u_i \vert (1- \frac{k}{h}\vert u_i \vert) \tilde{W_i}
+ \end{equation}
+ \noindent and the limiter is applied to wave $W_i = q_i - q_{i-1}$ i.e. traveling at speed $u(x)$, such that
+\begin{equation}
+ \tilde{W_i} =
+  \left\{ \begin{array}{c}
+limiter(W_i , W_{i-1}) , \, \, \, \, u_i > 0\\
+limiter(W_i , W_{i+1}) , \, \, \, \, u_i < 0\end{array}\right 
+\end{equation}
+Clearly, when $\tilde{W_i} = W_i$ the method is reduced to upwind + second order correction, i.e. Lax-Wendroff method. 
+On notation: $h,k$ are mesh spaces for the coarse coordinate and time grids respectively, and $u^+ (x) = max(u(x),0)$ and $u^- (x)=min(u(x),0)$ at $x$.
+
+\subsection{determining refinement - error estimation}\label{whentorefine}
+The idea behind the refinement step comes from first determining where a refinement may be useful.  
+If the solution $q(x,t)$ is smooth enough, we assume that method $D$ (application of eqn(\ref{hires})) has accuracy $O(s)$ in both 
+space and time. The local truncation error is $q(x,t+k) -D q(x,t) = \tau(x,t) + k O(k^{s+1}+h^{s+1}))$ where $\tau$ is the leading error.
+Taking two time steps suggests $q(x,t+2k) -D^2 q(x,t) = 2\tau(x,t) + k O(k^{s+1}+h^{s+1}))$.
+Now, coarsen the grid to have space and time widths $2h$, $2k$ and let the differencing scheme be called $D_{2h}$ in this case.
+The local truncation error in this case reads $q(x,t+2k) -D_{2h} q(x,t) = 2^{s+1}\tau(x,t) + O(h^{s+2})$.
+Thus, an error growth estimate at time $t$ can be formed by taking the difference in the error taking two steps with the regular integration scheme, and a single large step using every other grid point:
+\begin{equation}
+\frac{D^2 q(x,t) - D_{2h} q(x,t)}{2^{s+1}-2} = \tau(x,t) + O(h^{s+2}) \, .
+\end{equation}
+The difference between the solutions obtained on the two grids at each point is proportional to the local truncation error at that point.
+At coarse cells where the difference between the two sets of values exceed some tolerance, all four cells contained in the real grid are flagged as requiring refinement.
+See \cite{berg-coll} for more details.
+{\it Clustering} is simply to fill gaps in neighboring cells flagged for refinement.
+Should there be a cell not flagged for refinement between cells that require refinement, the cell in between will be refined as well because in the next step it is likely refinement will be required.
+A buffer zone around the flagged cells is added to track features of interest in the refined region.
+This buffer zone must be affiliated with the number of time steps evaluated at a particular level.
+If a patch at level $L$ is refined by even integer $R_L$, then the time-step is equally refined implying that $R_L$ steps must be taken on the refined grid at level $L+1$ for each step on grid at level $L$.
+
+\subsection{assigning values to new fine grid points}
+Once regions where a fine grid are determined, values must be assigned to the fine grid points.
+Space-time interpolation is needed to supply values for the fine grid because more time steps are taken on the fine grid  than the coarse grid and there are no coarse grid values available at intermediate times.
+This is achieved through a linear interpolation step with known coarse grid values and these values are available since we advance the coarse grid first as stated in the algorithm.
+
 \subsection{Flux updates on refined and coarse meshes}
-The idea behind the refinement step comes from first determining where a refinement may be useful, see section \ref{whentorefine} for details.  
-Here we explain how to preserve conservation of flux at grid interfaces and refer to Fig \ref{fig21}.
-There are essentially three cases to consider: coarse cell to coarse cell, fine cell to fine cell, and coarse cell to fine cell.
+After finishing the recursive step creating the fine grid structure, how to evolve the newly refined grid needs to be considered.
+To evolve, conservation of fluxes at grid interfaces is required.
+We refer to Fig \ref{fig21} for this discussion.
+There are essentially three cases to consider: coarse cell to coarse cell, fine cell to fine cell, and overlapping coarse cell and fine cell regions.
 Let $F_i$ be the flux at the left edge of coarse cell $i$.
 This is different notation than what we typically wrote in class, $F_{i-\frac{1}{2}}$.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=.6\textwidth]{berg-lev-fig21}
+   \caption{Essential figure for flux adapting Cartesian grids.
+The top grid is the normal coarse grid we are used to using with fluxes indicated.
+The middle diagram shows the case where a fine grid overlays a coarse grid and the interface region of fine and coarse grids.
+Recall that $2\hat{h}=h$ and $2\hat{k}=k$.
+The bottom diagram depicts the ghost cell region imposed on the coarse cell interface as well as the fine grid fluxes needed to bridge the interface.}
+    \label{fig21}
+\end{figure}
 
-Updating between coarse grid cells is simply:
+Updating between coarse grid cells is, to lowest order, simply:
 \begin{equation}
@@
 In regions where the coarse and fine grids overlap, care must be taken. Two ghost cells are introduced, $\hat{q}_{m+1},\hat{q}_{m+2}$. The values in these 
-cells are decided by interpolating the coarse values  $q_{i}^{0}, q_{i}^{1}$. At the final time (completed time step)  $q_{i}^{1}$ is replaced by the average of the 
+cells are decided by evaluating a polynomial (determined by interpolating the coarse values $q_{i}^{0}, q_{i}^{1}$)  at these fine grid locations.
+At the final time (completed time step)  $q_{i}^{1}$ is replaced by the average of the
 fine grid values in the overlapped region:
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=.65\textwidth]{berg-lev-fig21}
-   \caption{Essential figure for flux adapting Cartesian grids.
-The top grid is the normal coarse grid we are used to using with fluxes indicated.
-The middle diagram shows the case where a fine grid overlays a coarse grid and the interface region of fine and coarse grids.
-Recall that $2\hat{h}=h$ and $2\hat{k}=k$.
-The bottom diagram depicts the ghost cell region imposed on the coarse cell interface as well as the fine grid fluxes needed to bridge the interface.}
-    \label{fig21}
-\end{figure}
-
-\subsection{Updating grid interfaces with wave propagation}
-For conservation laws we have developed wave propagation methods in class whereby a Riemann problem is solved at each interface between grid cells.
-These methods can be extended beyond the linear accuracy to second order accuracy and controlled with limiters where smooth to discontinuous transitions occur.
+\subsection{updating grid interfaces with wave propagation -correction step}
+With flux-differencing to ensure conservation, a new coarse grid value is updated by an average of fine-grid values in any cell covered by a fine grid.
+The key to conservation is that flux into coarse cells is accounted for by flux out of adjacent fine cells, and vice versa, as described in the previous section.
 Wave propagation algorithms are written in a manner that they can be extended to hyperbolic problems not in conservation form retaining wave features but with no flux function.
-
-With flux-differencing to ensure conservation a new coarse grid value is updated by an average of fine-grid values in any cell covered by a fine grid.
-The key to conservation is that flux into coarse cells is accounted for by flux out of adjacent fine cells, and vice versa.
 For wave-propagation algorithms, a similar correction is needed for the waves to yield conservation.
@@
 
-Whether conservative or non-conservative systems are treated, second-order corrections are still written as flux-differences and utilize the flux correction as eqn(\ref{fluxcorrect}). 
+Recall from class that $A^+ \Delta q_{i-\frac{1}{2}}$ measures the net effect of all right going waves present from $x_{i-\frac{1}{2}}$, and $A^- \Delta q_{i-\frac{1}{2}}$ measures the net effect of all left going waves from the same interface.
+We call these {\it fluctuations}.
+Whether conservative or non-conservative systems are treated, second-order corrections are still written as flux-differences. 
 However, the first-order upwind terms written in terms of the fluctuations must be handled differently. 
-
-To maintain conservation we must {\it first} solve the Riemann problem between the ghost cell value $\hat{q}_{m+1}^{0}$ on the fine grid and the coarse grid value $q_{j}^{0}$, and add to the coarse cell value $q_{j}^{1}$ the resulting total fluctuation $A^{-}\Delta q + A^{+}\Delta q$ weighted by $\hat{k}/h = 1/2$ since the time step is $\hat{k}$ while the cell size is $h$.
+To maintain conservation we must {\it first} solve the Riemann problem between the ghost cell value $\hat{q}_{m+1}^{0}$ on the fine grid and the coarse grid value $q_{j}^{0}$, and add to the coarse cell value $q_{j}^{1}$ the resulting total fluctuation (dropped indices) $A^{-}\Delta q + A^{+}\Delta q$ weighted by $\hat{k}/h = 1/2$ since the time step is $\hat{k}$ while the cell size is $h$.
 {\it Second} we must also solve a Riemann problem on the fine grid between $\hat{q}_{m+1}^{1}$ and $q_{j}^{0}$
@@
 
-The correction step extends to an arbitrary hyperbolic system where we use a Riemann solver to obtain $A^{-}\Delta q$ and  $A^{+}\Delta q$ from the two states $\hat{q}_{m+1}^{0}$ and $q_{j}^{0}$.
+The correction step extends to an arbitrary hyperbolic system (i.e.
+see \ref{linsys} for linear hyperbolic system of PDEs) where we use a Riemann solver to obtain $A^{-}\Delta q$ and  $A^{+}\Delta q$ from the two states $\hat{q}_{m+1}^{0}$ and $q_{j}^{0}$.
 This step is made in each of the $R$ time steps on the refined grid within the single coarse-grid step, where $R$ is the refinement ratio.
@@
 
-\noindent The fix-up algorithm:
+\noindent In summary, the correction algorithm reads:
 \begin{description}
@@
 
-\subsection{Pseudo-code for AMR}
-\subsection{Comment on determining refinement - error estimation}\label{whentorefine}
-If the solution $q(x,t)$ is smooth enough, assume that our difference method $D$ has order of accuracy $s$ in both 
-space and time, then the local truncation error is $q(x,t+k) -D q(x,t) = \tau(x,t) + k O(k^{s+1}+h^{s+1}))$ where $\tau$ is the leading error.
-Taking two time steps suggests $q(x,t+2k) -D^2 q(x,t) = 2\tau(x,t) + k O(k^{s+1}+h^{s+1}))$.
-Now, coarsen the grid to have space and time widths $2h$, $2k$ and let the differencing scheme be called $D_{2h}$ in this case.
-The local truncation error in this case reads $q(x,t+2k) -D_{2h} q(x,t) = 2^{s+1}\tau(x,t) + O(h^{s+2})$.
-Thus, an error growth estimate at time $t$ can be formed by taking the difference in the error taking two steps with the regular integration scheme, and a single large step using every other grid point:
-\begin{equation}
-\frac{D^2 q(x,t) - D_{2h} q(x,t)}{2^{s+1}-2} = \tau(x,t) + O(h^{s+2}) \, .
-\end{equation}
-The values on a grid at a given level are projected, i.e.
-Richardson extrapolation, onto a virtual grid coarsened by a factor of two in each direction.
-The solutions on both grids are advanced in time: the original grid for two time steps, the coarsened grid for one step using a time step twice as large.
-The difference between the solutions obtained on the two grids at each point is proportional to the local truncation error at that point.
-At coarse cells where the difference between the two sets of values exceed some tolerance, all four cells contained in the real grid are flagged as requiring refinement.
-One disadvantage of this procedure is that it always predicts a large error in the neighborhood of captured discontinuities.
-It is easy to construct examples for which the procedure outlined above will give values on the coarsened grid which differ pointwise by an amount independent of the mesh spacing in the neighborhood of a shock.
-See \cite{berg-coll} for more details.
-A buffer zone around the flagged cells is added to track features of interest in the refined region.
-This buffer zone must be affiliated with the number of time steps evaluated at a particular level.
-If a patch at level $L$ is refined by even integer $R_L$, then the time-step is equally refined implying that $R_L$ steps must be taken on the refined grid at level $L+1$ for each step on grid at level $L$.
-
 \subsection{Note on boundary conditions}
@@
 \section{Examples of 1D AMR}
-\subsection{scalar advection}
-The simplest problem (and most boring) is the 1D scalar advection equation
+\subsection{variable coefficient}\label{color}
+Here we state a 1D scalar problem based on a variable coefficient velocity term.The {\it color} equation is the problem formed by solving the following Riemann problem at the interface $x_{i-\frac{1}{2}}$ between cells $i-1$ and $i$:
+
 \begin{equation}
-q(x,t)_{t} + \bar{u} q(x,t)_{x}=0
+ q(x,t)_{t} + u(x) q(x,t)_{x}=0
  \end{equation}
-where $\bar{u}$ is a constant representing the velocity of displacement. Let $\bar{u}>0$ for simplicity (right going).
-The Riemann problem in this case consists of adding the initial conditions:
+
 \begin{equation}
@@
 \left\{ \begin{array}{c}
-q_l , \, \, \, \, x<0\\
-q_r , \, \, \, \, x>0\end{array}\right. 
+q_{i-1} , \, \, \, \, x<x_{i-\frac{1}{2}}\\
+q_{i} , \, \, \, \, x>x_{i-\frac{1}{2}}\end{array}\right
+ \quad 
+,
+\quad u(x)=
+ \left\{ \begin{array}{c}
+u_{i-1} , \, \, \, \, x<x_{i-\frac{1}{2}}\\
+u_{i} , \, \, \, \, x>x_{i-\frac{1}{2}}\end{array}\right 
 \end{equation}
+\noindent and the sign of $u(x)$ arbitrary for now.
 
-\noindent Here the coefficient matrix is the number $\bar{u}$ which has eigenvalue $\lambda^1 = \bar{u}$ and eigenvector $r^1 =1$ and the jump discontinuity determined by $q_r - q_l$ propagates with speed $\lambda^1$ along characteristics.
-The solution is
-\begin{equation}
-q(x,t):= \phi(x-\lambda^1 t) \, .
-\end{equation}
-
-\subsection{variable coefficient (color equation)}
-We study here the 1D scalar problem of the form
-\begin{equation}
-q(x,t)_{t} + u(x) q(x,t)_{x}=0
-\end{equation}
-\noindent where now the velocity is allowed to vary as a function of its position. This is sometimes called the {\it color} equation.
-
-\subsection{nonlinear scalar (Burgers)}
-We study here the 1D systems derived from the conservative, 
-\begin{equation}
-q(x,t)_{t} + f(q(x,t))_{x}=0
-\end{equation}
-which can be cast in non-conservative, quasilinear form 
- \begin{equation}
-q(x,t)_{t} + f'(q(x,t))q(x,t)_{x}=0 .
-\end{equation}
-In Burgers inviscid equation, $f(q(x,t))=\frac{1}{2}q^2$.
-
-\subsection{linear system (acoustics)}
+\subsection{linear system (acoustics)} \label{linsys}
 We study here the 1D systems of the form
@@
 \noindent and $A$ satisfies hyperbolicity conditions.
-
-\subsection{nonlinear system (shallow water or acoustics with pressure term)}
-We use the formulation in chapter 13 of \cite{levFVMHP} to describe the shallow water equations.
-So,
-
-\begin{equation}
-\left( \begin{array}{c}
-h  \\
-h u\end{array} \right)_{t} + 
-\left( \begin{array}{c} 
-hu \\
-hu^2 + \frac{1}{2}gh^2\end{array} \right)_{x} = 0
-\end{equation}
-
-\noindent where $h$ is the height (or depth) of the fluid, $u$ is the horizontal component of the velocity, and $hu$ is the discharge -i.e.
-the flow rate of the fluid past a point.
-One can assign the state variables $(q^1,q^2)$, and the flux $f$ as follows:
-
-\begin{equation}
-q(x,t)=\left( \begin{array}{c}
-h  \\
-h u\end{array} \right)
-=
-\left( \begin{array}{c}
-q^1  \\
-q^2\end{array} \right) 
-\end{equation}
-\noindent and
-
-\begin{equation}
-f(q(x,t))=
-\left( \begin{array}{c} 
-hu \\
-hu^2 + \frac{1}{2}gh^2\end{array} \right)
-= 
-\left( \begin{array}{c} 
-q^2 \\
-(q^2)^2 / q^1 + \frac{1}{2}g (q^1)^2\end{array} \right)
-\end{equation}
-\noindent to be consistent with state notation from previous sections of this report.
 
@@
 implementations are available to anyone who wants them.
-
-%kr -just let the TOC do the outline for us and track our changes at compile time 
-%also, I added a couple of bullets since our discussion this afternoon
-%\section{Outline}
-%\begin{itemize}
-%\item Overview of paper
-%\begin{itemize}
-%\item Description of AMR, Figure 2.1 from Berger-Leveque paper.
-%\item Wave propagation form for 1-d equations. Updating on grid interfaces, section 4 of paper
-%\item pseudo-code for algorithm, similar to that on page 2310 of paper.
-%\item comment on error estimation -determining refinement
-%\item notes on: flagging cells, boundary conditions
-%\end{itemize}
-%\item Examples of 1D AMR
-%\begin{itemize}
-%\item scalar advection
-%\item linear system (e.g. Acoustics)
-%\item variable coefficient (e.g. Color equation)
-%\item nonlinear scalar (burgers)
-%\item nonlinear system (shallow water or acoustics with pressure term)
-%\end{itemize}
-%\item Results of Numerical Experiments for the 1D cases
-%\item Software 
-%
-%\end{itemize}
 

### 2015-03-08 paper_draft1.tex
paper -changed outline slightly and edited

@@
 
-\subsection{Flux updates on refined and coarse meshes}
+\subsection{flux updates on refined and coarse meshes}
 After finishing the recursive step creating the fine grid structure, how to evolve the newly refined grid needs to be considered.

### 2015-03-08 paper_draft1.tex
Modified tex file

@@
 
-%\setlength{\textwidth}{6.2in}
-%\setlength{\oddsidemargin}{0.2in}
-%\setlength{\evensidemargin}{0in}
-%\setlength{\textheight}{8.9in}
-%\setlength{\voffset}{-1.0in}
 %\setlength{\parindent}{20pt}
-%\setlength{\parindent}{1cm}
+\setlength{\parindent}{1cm}
 \setlength{\textwidth}{6.2in}
@@
 \newcommand{\mb}{\mathbb}
+\newcommand{\mc}{\mathcal}
 
-%\setlength{\parskip}{2mm}
+\newcommand{\reals}{\mathbb{R}}
+
+\setlength{\parskip}{2mm}
 \renewcommand{\theenumi}{\alph{enumi}}
@@
 
-\section{Overview of Paper}
-An adaptive mesh refinement strategy that uses rectangular patches over Cartesian grids to refine both space and time coordinates is useful for modeling and tracking regions where the solutions are not smooth such as exhibited around shocks.
-We present an AMR algorithm in the next section, and provide details in subsequent sections for the various steps.
+\section{Introduction}
+We describe an adaptive mesh refinement (AMR) strategy for the solution of hyperbolic systems of conservation laws.
+The solutions of these equations are often smooth and easily approximated over large portions of their domain, but contain locally isolated regions with steep gradients, shocks or discontinuities.
+Our AMR strategy models and tracks such regions, by using rectangular patches over Cartesian grids to refine both the space and time coordinates.
 
-\section{Pseudo-code for AMR}
-\noindent Steps for the AMR algorithm:
-\begin{enumerate}
-\item{initialize coarse grid}
-\item{evolve time on coarse grid}
-\item{{\it recurse}: estimate error, create fine grid}
-\begin{itemize}
-\item{cell flagging}
-\item{clustering}
-\item{fine grid generation}
-\end{itemize}
-\item{solve Riemann on refined grid levels}
-\item{correction step to ensure conservation}
-\item{go to step {\it b} }
-\end{enumerate}
+\section{The AMR algorithm}
+\noindent
+In this paper, we consider only one-dimensional systems.
+The coarse grid consists of a collection of intervals or cells that cover the entire domain, while refinements cover a subset of the domain and have finer cell-widths.
+If the cell-width in a fine grid is refined by an even integer $R_L$, then the time-step is also refined by the same factor, so that the ratio $\Delta t/\Delta x$ remains unchanged and for every single time-step on the coarse grid, $R_L$ time steps must be taken on the fine grid.
 
-\subsection{wave propagation algorithm to evolve time}
-After initializing the discrete coarse grid, a standard high resolution wave propagation including limiter corrections to evolve our Riemann problem is employed.
-The method reads,  i.e.
-for the {\it color} eqn (see \ref{color}):
-\begin{equation} \label{hires}
- q_{i}^{n+1} = q_{i}^{n} - \frac{k}{h}(u_{i}^{+}(q_{i}^{n}-q_{i-1}^{n})+u_{i}^{-}(q_{i+1}^{n}-q_{i}^{n})) - \frac{k}{h}(\tilde{F_{i+1}} - \tilde{F_{i}})
- \end{equation}
- \noindent where 
- \begin{equation}
-\tilde{F_{i}} = \frac{1}{2}\vert u_i \vert (1- \frac{k}{h}\vert u_i \vert) \tilde{W_i}
- \end{equation}
- \noindent and the limiter is applied to wave $W_i = q_i - q_{i-1}$ i.e. traveling at speed $u(x)$, such that
-\begin{equation}
- \tilde{W_i} =
-  \left\{ \begin{array}{c}
-limiter(W_i , W_{i-1}) , \, \, \, \, u_i > 0\\
-limiter(W_i , W_{i+1}) , \, \, \, \, u_i < 0\end{array}\right 
-\end{equation}
-Clearly, when $\tilde{W_i} = W_i$ the method is reduced to upwind + second order correction, i.e. Lax-Wendroff method. 
-On notation: $h,k$ are mesh spaces for the coarse coordinate and time grids respectively, and $u^+ (x) = max(u(x),0)$ and $u^- (x)=min(u(x),0)$ at $x$.
+An error estimation procedure based on Richardson extrapolation, described in more detail in section \ref{whentorefine}, is used to flag the cells which need refinement.
+Flagged cells are clustered into patches, and a fine grid is generated for each patch (including a buffer zone).
+A finite volume method in wave-propagation form is used to advance the solution on the coarse grid over a single time-step, and then the solution on the fine grid(s) is advanced over $R_L$ time steps to catch-up.
+
+Every $K$ time steps, the fine grids are regenerated, and the error estimation procedure is re-applied to capture the movement of the discontinuities. The refinement and solution process is repeated.
+
+Each of the above steps is described in more detail below.
+
+\subsection{Advance solution over coarse grid}
+After initializing the discrete coarse grid, the first step is to advance the solution over a single time-step on the coarse grid.
+A standard high resolution wave propagation method (with limiter corrections) is used to solve the Riemann problem.
+
+Consider a linear system
+\[
+q_t + A(x) q_x = 0,
+\]
+where $q \in \reals^m$ and $A \in \reals^{m \times m}$ is diagonalizable with real eigenvalues.
+On the cell $[x_{i-1/2},x_{i+1/2}$, the matrix $A(x)$ is approximated by a matrix $A_{i-1}$ with eigenvalues $\lambda^1_{i-1}, \ldots, \lambda^m_{i-1}$.
+Then for the Riemann problem at $x_{i-1/2}$, we decompose $q_i - q_{i-1}$ into waves $\mc{W}^p_{i}, p = 1,2,\ldots,m$ in such a way that the left-going waves are eigenvectors of the matrix $A_{i-1}$, traveling with speeds $\lambda^p_{i-1} <0$, while the right-going waves are eigenvectors of $A_i$ traveling with speeds $\lambda^p_i>0$.
+The update formula is then
+\beq \label{waveprop}
+q_i^{n+1} = q_i^n - \frac{k}{h}
+\sum\limits_{p=1}^m \left[ (\lambda_i^p)^+ \mc{W}_i^p + (\lambda_{i+1}^p)^- \mc{W}_{i+1}^p\right]
+- \frac{k}{h} \left( \tilde{F}_{i+1} - \tilde{F}_i \right)
+\eeq
+where $k$ is the length of the time-step and $h$ is the cell-width in the spatial grid, and for any real number $a$, $a^+ = \max\{a,0\}$ and $a^- = \max\{-a,0\}$.
+
+The summation term gives the first-order upwind method, while the fluxes $\tilde{F}_i$ are the second-order corrections defined by
+\beq
+\tilde{F}_i = \frac{1}{2} \sum\limits_{p=1}^m
+\left| \lambda_i^p\right| \left( 1-\frac{k}{h} \left| \lambda_i^p\right| \right) \tilde{\mc{W}}_{i+1}
+\eeq
+where $\tilde{W}_{i+1}^p$ is some limited version of the wave $\mc{W}_i^p$.
+When $\tilde{W_i} = W_i$, the method is reduced to upwind + second order correction, i.e. Lax-Wendroff method.
+
+This method is extended to nonlinear systems using the Roe approximate Riemann solver, which linearizes the problem at each cell-interface in such a way that conservation is guaranteed.
+This method is symbolically written as
+\begin{equation*}
+q_i^{n+1} = q_i^n - \frac{k}{h}
+\sum\limits_{p=1}^m \left[ \mc{A}^+\Delta(q_{i}) + \mc{A}^-\Delta(q_{i+1})\right]
+- \frac{k}{h} \left( \tilde{F}_{i+1} - \tilde{F}_i \right)
+\end{equation*}
+where $\mc{A}^+\Delta(q_{i})$ represents the right-going fluctuation from the left interface of cell $i$, while $\mc{A}^-\Delta(q_{i})$ is the left-going fluctuation from the right interface of cell $i$.
 
@@
 
+ Steps for the AMR algorithm:
+\begin{enumerate}
+\item{initialize coarse grid}
+\item{evolve time on coarse grid}
+\item{{\it recurse}: estimate error, create fine grid}
+\begin{itemize}
+\item{cell flagging}
+\item{clustering}
+\item{fine grid generation}
+\end{itemize}
+\item{solve Riemann on refined grid levels}
+\item{correction step to ensure conservation}
+\item{go to step {\it b} }
+\end{enumerate}
+
 \section{Examples of 1D AMR}
@@
 
+ The method reads,  i.e. for the {\it color} eqn (see \ref{color}):
+\begin{equation} \label{hires}
+ q_{i}^{n+1} = q_{i}^{n} - \frac{k}{h}(u_{i}^{+}(q_{i}^{n}-q_{i-1}^{n})+u_{i}^{-}(q_{i+1}^{n}-q_{i}^{n})) - \frac{k}{h}(\tilde{F_{i+1}} - \tilde{F_{i}})
+ \end{equation}
+ \noindent where 
+ \begin{equation}
+\tilde{F_{i}} = \frac{1}{2}\vert u_i \vert (1- \frac{k}{h}\vert u_i \vert) \tilde{W_i}
+ \end{equation}
+ \noindent and the limiter is applied to wave $W_i = q_i - q_{i-1}$ i.e. traveling at speed $u(x)$, such that
+\begin{equation}
+ \tilde{W_i} =
+  \left\{ \begin{array}{c}
+limiter(W_i , W_{i-1}) , \, \, \, \, u_i > 0\\
+limiter(W_i , W_{i+1}) , \, \, \, \, u_i < 0\end{array}\right. 
+\end{equation}
+
 \begin{equation}
@@
 q_{i-1} , \, \, \, \, x<x_{i-\frac{1}{2}}\\
-q_{i} , \, \, \, \, x>x_{i-\frac{1}{2}}\end{array}\right
+q_{i} , \, \, \, \, x>x_{i-\frac{1}{2}}\end{array}\right.
  \quad 
@@
 u_{i-1} , \, \, \, \, x<x_{i-\frac{1}{2}}\\
-u_{i} , \, \, \, \, x>x_{i-\frac{1}{2}}\end{array}\right 
+u_{i} , \, \, \, \, x>x_{i-\frac{1}{2}}\end{array}\right. 
 \end{equation}

### 2015-03-09 paper_draft1.tex
paper -correct some errors -add some comments

@@
 \section{The AMR algorithm}
-\noindent
-In this paper, we consider only one-dimensional systems.
+\noindent In this paper, we consider only one-dimensional systems.
 The coarse grid consists of a collection of intervals or cells that cover the entire domain, while refinements cover a subset of the domain and have finer cell-widths.
 If the cell-width in a fine grid is refined by an even integer $R_L$, then the time-step is also refined by the same factor, so that the ratio $\Delta t/\Delta x$ remains unchanged and for every single time-step on the coarse grid, $R_L$ time steps must be taken on the fine grid.
-
 An error estimation procedure based on Richardson extrapolation, described in more detail in section \ref{whentorefine}, is used to flag the cells which need refinement.
@@
 A finite volume method in wave-propagation form is used to advance the solution on the coarse grid over a single time-step, and then the solution on the fine grid(s) is advanced over $R_L$ time steps to catch-up.
-
-Every $K$ time steps, the fine grids are regenerated, and the error estimation procedure is re-applied to capture the movement of the discontinuities. The refinement and solution process is repeated.
-
+Every $R$ time steps, the fine grids are regenerated, and the error estimation procedure is re-applied to capture the movement of the discontinuities.
+The refinement and solution process is repeated.
 Each of the above steps is described in more detail below.
@@
 
-Consider a linear system
-\[
-q_t + A(x) q_x = 0,
-\]
+\noindent Consider a linear system $q_t + A(x) q_x = 0$,
 where $q \in \reals^m$ and $A \in \reals^{m \times m}$ is diagonalizable with real eigenvalues.
-On the cell $[x_{i-1/2},x_{i+1/2}$, the matrix $A(x)$ is approximated by a matrix $A_{i-1}$ with eigenvalues $\lambda^1_{i-1}, \ldots, \lambda^m_{i-1}$.
-Then for the Riemann problem at $x_{i-1/2}$, we decompose $q_i - q_{i-1}$ into waves $\mc{W}^p_{i}, p = 1,2,\ldots,m$ in such a way that the left-going waves are eigenvectors of the matrix $A_{i-1}$, traveling with speeds $\lambda^p_{i-1} <0$, while the right-going waves are eigenvectors of $A_i$ traveling with speeds $\lambda^p_i>0$.
+On the cell $[x_{i-1/2},x_{i+1/2}]$, the matrix $A(x)$ is approximated by a matrix $A_{i-1}$ for cell $i-1$ with eigenvalues $\lambda^1_{i-1}, \ldots, \lambda^m_{i-1}$.
+Then for the Riemann problem at $x_{i-1/2}$, we decompose $q_i - q_{i-1}$ into waves $\mc{W}^p_{i}\, , p = 1,\ldots,m$ in such a way that the left-going waves are eigenvectors of the matrix $A_{i-1}$, traveling with speeds $\lambda^p_{i-1} <0$, while the right-going waves are eigenvectors of $A_i$ traveling with speeds $\lambda^p_i>0$.
 The update formula is then
@@
 
-The summation term gives the first-order upwind method, while the fluxes $\tilde{F}_i$ are the second-order corrections defined by
+\noindent The summation term gives the first-order upwind method, while the fluxes $\tilde{F}_i$ are the second-order corrections defined by
 \beq
@@
 
-This method is extended to nonlinear systems using the Roe approximate Riemann solver, which linearizes the problem at each cell-interface in such a way that conservation is guaranteed.
+\noindent This method is extended to nonlinear systems using the Roe approximate Riemann solver, which linearizes the problem at each cell-interface in such a way that conservation is guaranteed.
 This method is symbolically written as
@@
 The idea behind the refinement step comes from first determining where a refinement may be useful.  
-If the solution $q(x,t)$ is smooth enough, we assume that method $D$ (application of eqn(\ref{hires})) has accuracy $O(s)$ in both 
+If the solution $q(x,t)$ is smooth enough, we assume that method $D$ (application of eqn(\ref{waveprop})) has accuracy $O(s)$ in both 
 space and time. The local truncation error is $q(x,t+k) -D q(x,t) = \tau(x,t) + k O(k^{s+1}+h^{s+1}))$ where $\tau$ is the leading error.
@@
 Once regions where a fine grid are determined, values must be assigned to the fine grid points.
-Space-time interpolation is needed to supply values for the fine grid because more time steps are taken on the fine grid  than the coarse grid and there are no coarse grid values available at intermediate times.
-This is achieved through a linear interpolation step with known coarse grid values and these values are available since we advance the coarse grid first as stated in the algorithm.
+Current time fine grid values are assigned by evaluating a linear interpolation akin to flux limiting between coarse cell values in neighboring cells.
+Intermediate time values on the fine grid are assigned by evaluating a bilinear space-time interpolation based on coarse grid values between neighboring cells at the current and subsequent time.
+This approach is needed because more time steps are taken on the fine grid  than the coarse grid and there are no coarse grid values available at intermediate times.
 
 \subsection{flux updates on refined and coarse meshes}
-After finishing the recursive step creating the fine grid structure, how to evolve the newly refined grid needs to be considered.
+After recursively creating the fine grid, how to evolve the newly refined grid needs to be considered.
 To evolve, conservation of fluxes at grid interfaces is required.
@@
 
-Updating between coarse grid cells is, to lowest order, simply:
+\noindent Updating between coarse grid cells is, to lowest order, simply:
 \begin{equation}
@@
 
-In regions that contain $m$ adjacent single level refined cells let the lattice spacing be denoted by $\hat{h},\hat{k}$.
+\noindent In regions that contain $m$ adjacent single level refined cells let the lattice spacing be denoted by $\hat{h},\hat{k}$.
 We have, in the stated order, $\forall i=1,m$
@@
 \end{equation}
-\noindent in the refined cells where we assume each refinement is $2X$.
+\noindent in the refined cells where we assume each refinement is $2X$ as in the figure.
 
-In regions where the coarse and fine grids overlap, care must be taken. Two ghost cells are introduced, $\hat{q}_{m+1},\hat{q}_{m+2}$. The values in these 
-cells are decided by evaluating a polynomial (determined by interpolating the coarse values $q_{i}^{0}, q_{i}^{1}$)  at these fine grid locations.
-At the final time (completed time step)  $q_{i}^{1}$ is replaced by the average of the
-fine grid values in the overlapped region:
+\noindent In regions where the coarse and fine grids overlap, care must be taken. Two ghost cells are introduced, $\hat{q}_{m+1},\hat{q}_{m+2}$. The values in these 
+cells are decided by evaluating a polynomial at these fine grid locations determined by interpolating coarse grid values (as stated earlier).
+To complete the time step,  $q_{i}^{1}$ is replaced by the average of the fine grid values in the overlapped region:
 \begin{equation}
@@
 For wave-propagation algorithms, a similar correction is needed for the waves to yield conservation.
-The wave-propagation form can be used to update the values at the interface between fine and coarse grid cells on each grid independently using Òghost-cellÓ values as needed near grid interfaces.
+The wave-propagation formis used to update the values at the interface between fine and coarse grid cells on each grid independently using Òghost-cellÓ values as needed near grid interfaces.
 
-Recall from class that $A^+ \Delta q_{i-\frac{1}{2}}$ measures the net effect of all right going waves present from $x_{i-\frac{1}{2}}$, and $A^- \Delta q_{i-\frac{1}{2}}$ measures the net effect of all left going waves from the same interface.
+\noindent Recall from class that $A^+ \Delta q_{i-\frac{1}{2}}$ measures the net effect of all right going waves present from $x_{i-\frac{1}{2}}$, and $A^- \Delta q_{i-\frac{1}{2}}$ measures the net effect of all left going waves from the same interface.
 We call these {\it fluctuations}.
@@
 
-The correction step extends to an arbitrary hyperbolic system (i.e.
+\noindent The correction step extends to an arbitrary hyperbolic system (i.e.
 see \ref{linsys} for linear hyperbolic system of PDEs) where we use a Riemann solver to obtain $A^{-}\Delta q$ and  $A^{+}\Delta q$ from the two states $\hat{q}_{m+1}^{0}$ and $q_{j}^{0}$.
